\bf Title here

### 2020-05-19 paper/paper.Rmd
write GOG; explore post-run diagnostics using vis

---
title: Title here

# to produce blinded version set to 1
blinded: 0

authors: 
- name: Author 1
  thanks: The authors gratefully acknowledge ...
  affiliation: Department of YYY, University of XXX

- name: Author 2
  affiliation: Department of ZZZ, University of WWW

keywords:
- 3 to 6 keywords
- that do not appear in the title

abstract: |
  1. check consistency of using PP for projection pursuit and PPI for projection pursuit index

bibliography: biblio.bib
output: rticles::asa_article
---

@@

load(here::here("data/temp.rda"))
load(here::here("data/data_mult.rda"))
load(here::here("data/holes_1d_geo.rda"))
load(here::here("data/holes_2d_geo.rda"))
load(here::here("data/holes_2d_better.rda"))
load(here::here("data/holes_2d_better_max_tries.rda"))
load(here::here("data/holes_2d_better_random.rda"))
load(here::here("data/holes_2d_geo_polish.rda"))
load(here::here("data/holes_2d_better_polish.rda"))
load(here::here("data/holes_2d_better_max_tries_polish.rda"))
load(here::here("data/holes_2d_better_random_polish.rda"))
load(here::here("data/interrupt_yes.rda"))
load(here::here("data/interrupt_no.rda"))

@@

# Recording the guided tour

@@

@@

## add something about general vis

The creation of the global object facilitates the diagnostics of the optimisation in the projection pursuit guided tourr. Different diagnostic plots could be made to understand the optimisation **[pretty cheesy here]**

@@

## index vs time plots

The tracing plot is useful to explore the index value. Given a global object created, `explore_trace_all()` plots the index value of all the bases.

```{r echo = TRUE}
holes_2d_geo %>% explore_trace_all(magnify = TRUE)
holes_2d_geo %>% explore_trace_interp()
```

## target basis vs interpolation steps, index vs time

## low-d representation, PCA

>>>>

---
title: Title here
blinded: 0
authors:

- name: Author 1
  thanks: The authors gratefully acknowledge ...
  affiliation: Department of YYY, University of XXX
- name: Author 2
  affiliation: Department of ZZZ, University of WWW
keywords:
- 3 to 6 keywords
- that do not appear in the title
abstract: |
  1. check consistency of using PP for projection pursuit and PPI for projection pursuit index 
bibliography: biblio.bib
output: rticles::asa_article
editor_options: 
  chunk_output_type: console
---

@@

load(here::here("data/temp.rda"))
load(here::here("data/data_mult.rda"))
load(here::here("data/holes_1d_geo.rda"))
load(here::here("data/holes_2d_geo.rda"))
load(here::here("data/holes_2d_better.rda"))
load(here::here("data/holes_2d_better_max_tries.rda"))
load(here::here("data/holes_2d_better_random.rda"))
load(here::here("data/holes_2d_geo_polish.rda"))
load(here::here("data/holes_2d_better_polish.rda"))
load(here::here("data/holes_2d_better_max_tries_polish.rda"))
load(here::here("data/holes_2d_better_random_polish.rda"))
load(here::here("data/holes_2d_pos.rda"))
load(here::here("data/interrupt_yes.rda"))
load(here::here("data/interrupt_no.rda"))

@@

# Iterative algorithm and its diagnostics

@@

## Diagnostics

Visualisatioin has been widely used for exploring and understanding data. Visualisation presents information in a graphicial manner and often allows people to see information they would otherwise not seen in the reporting of numerical summarisation. Visual diagnostics can be real-time or post-run. Real time diagnostic directly uses the data produced in the algorithm to produce visual representation and thus doesn't need to store the data.   This section focuses on the definition and production of post-run diagnoistics and the next section discusses real-time diagnostics.

Post-run diagnostics requires the data produced during the algorithm to be stored/ saved in order to produce plot diagnostics.

The graphical system in R is established based on the conception gramma of graphic [@wickham2010layered], where a graphic is defined using stacked layers in a coordination system.  A layer includes 1) the dataset that powers the plot; 2) a geometric object that represents the visual shape of the plot and 3) relevant statistical transformation if needed. An important concept in the gramma of graphic is *aesthetic mapping*. Aesthetic mapping links the variable in a dataset to information needed to produce a geometric object. For example, we map one variable on the x-axis and another on the y-axis to create a scatterplot. To create a boxplot, we first map one variable on the x-axis and then map the five point summary of another variable on the y-axis. This computation of five point summary from the origin variable is statistical transformation. This definition of graphic through layers provides advantages to produce complex plots since all the plots, however complex, can be decomposed into basic geometric objects shaped by the variable supplied.

This idea of decompositing a graph to basic elements inspires me to characterise the diagnostics of iterative algorithm in a similar fashion. The optimisation in many machine learning algorithms these days is iterative in nature, while remains as a black box. Being able to diagnose it visually allows researchers to have the tool to unfold the myth and thus provides more understand to the algorithm.

The concept of gramma of graphic requires a dataset to be supplied in making a plot, thus a global object needs to be created in the iterative algorithm. The variables will be mapped into element of a graphic to explore and thus should contain all the parameters of interest. The next section shows how a global object is created in projection pursuit guided tour.

@@

Given all the information of interest in a global object, the next thing is to design its visual representation that can diagnose our algorithm. In an iterative algorithm, one would be interested to know how one parameter changes as the algorithm iterates. The parameter could be could be the decision variable, the value of the optimisation function or other parameter that facilitate the algorithm. In projectio pursuit guided tour, apart from the decision variable projection basis, the value of index function (`index_val`), we are also interested to explore the effect the different searching methods, the neighbourhood parameter alpha, and the stage a particular observation is in (`info`). These are the variables that will be mapped into the diagnostic plot. The global object also has its time series nature since the observations are recorded as the algorithm progresses and thus can't be switch in rows. This time series structure is always hierachical and nested since each row can be labelled with the smallest unit `id` and up by the iterative structure of the algorithm. Take our example, in the global object, each row has an `id` label which is the smallest unit the observation is ordered. A larger ordering unit is `tries` since it is updated everytime a new target basis is found. A nested ordering unit is `loop`, which increases by one as searching method iterates and starts over at a new `tries`. These features explain the definition of the global object for projection pursuit guided tour in Figure \@ref(fig:glb-obj).

```{r glb-obj, out.width= "100%", out.height="20%", fig.cap="this is xxxx"}
knitr::include_graphics(path = here::here("figures/global_obj.png"))
```

@@

## Explore scalar parameters

The most interesting parameter to explore is the value of objective function. Given the structure of projection pursuit guided tour algorithm, whatever searching method we use, we could roughly divide the observation into three category: searching, updating and interpolating points.

- *Searching points* include the observations that ones recorded during the trials and errors in the searching algorithm to find the target basis. In one `tries`, there could be only a few searching points while towards the end of the algorithm, they can easily go to hundreds.

- *Updating points* are the observations for the target points and there are only one points per `tries`. We use "all searching points" to refer to the collection of both searching and updating points.

- *interpolation points* exist specifically in the guided tour in order to provide continuous animated view from one target basis to another, thus they are not included in the searching procedure. There are multiple points in one tries but it doesn't have `loop` value.

### Explore all searching points

As mentioned previously, the largest feature of exploring searching points is its uncertainty in the number per `tries`. This makes it difficult to map `id` on the x-axis since the first few tries that can be informative to the evolving of the algorithm occupies a small number of points on the graph while the large less informative search points towards the end occupies the vast majority of the plot space.

This motivates the use of summarised statistics. At each iteration, rather than knowing the value of *every* points, we are more interested to know a general summary of all the points and more importantly, the point with the largest `index_val` since it is the one that prescribe the interpolation and future search. Therefore, boxplot is a suitable candidate.

However, boxplot doesn't tells us the number of point in each box. By showing boxplot for all `tries`, we lose information on how long it takes for the search to find the target basis. We may still want to show the exact points of every point if there are only a few points. Therefore a cutoff point is placed as an argument to decise when to switch from point geometry to boxplot geometry.

This design is easy to implement with the concept of gramma of graphic. With the idea of layed gramma, we only need to subset the data and map it onto the either a point geometry or boxplot geometry. We can also add a layer with line geometry that connect the points with the largest `index_val` in each tries. This would show us which `tries` has the largest improvement.

A comparison of using scatter plot (all point geometry) and my new design is shown in Figure \@ref(fig:explore-all-search). As we can see the points for the first few tries on hte scatter plot are all squeezed in a tiny region, being nearly unseeable. While the plot on the right balances out the points in each `tries`. By linking the updating points for each `tries`, we observe that the largest improvement occurs in `tries = 5` where the number of searching points dramastically increased from 11 points in `tries = 4` to 86 points in `tries = 5`.

```{r explore-all-search, fig.cap="This is xxx"}
dt <- holes_2d_better_max_tries %>%
  filter(info != "interpolation") %>% 
  mutate(id = row_number())

p1 <- dt %>% 
  ggplot(aes(x = id, y = index_val, col = as.factor(tries))) + 
  geom_point()  +
  geom_line(data = dt %>% group_by(tries) %>% filter(index_val == max(index_val)),
            aes(group = 1)) 
  #theme(legend.position = "none")

dt_count <- dt %>%
  group_by(as.factor(tries)) %>%
  count() %>%
  rename(tries = `as.factor(tries)`)

p2 <- dt %>%
  ggplot(aes(x = as.factor(tries), y = index_val, col = as.factor(tries))) +
  geom_boxplot(data = dt %>% filter(tries %in% which(dt_count$n > 15))) +
  geom_point(data = dt%>% filter(tries %in% which(dt_count$n < 15))) +
  geom_line(data = dt %>% group_by(tries) %>% filter(index_val == max(index_val)),
            aes(group = 1)) 
  #theme(legend.position = "none")

(p1 | p2) & theme(legend.position = "bottom")

### Explore only interpolation points

While mapping `tries` to the x axis allows for viewing the magnitude of the interpolation and also its density, we can't really see the curvature of the interpolated path. Think this would be important when the index is no longer smooth and the interpolation will jump up and down. Thus the geom_point + geom_line specification is still preferred.

EXAMPLE: prevention on the decrese of interpolated value - interruption

EXAMPLE: comparison of interpolation in noisy index function

<!-- The tracing plot is useful to explore the index value. Given a global object created, `explore_trace_all()` plots the index value of all the bases.  -->

```{r}
# points is always included in the newest version
p1 <- holes_2d_better %>% 
  filter(info == "interpolation") %>% 
  ggplot(aes(x = tries, y = index_val, col = as.factor(tries))) +
  geom_point() + 
  geom_line(aes(group = 1))

p2 <- holes_2d_better %>% explore_trace_interp() + geom_point(aes(col = as.factor(tries)))

(p1 | p2)  &
  theme(legend.position = "bottom")

### Adding more variables to the mapping

For now we only include the iterator and `index_val` in the mapping of the plot, while more paramters of interest could be added to explore the effect their effect.

EXAMPLE: polishing - add method : compare with max.tries and without for search_better.

EXAMPLE: add alpha: compare the cooling system of the neighbourhood parameter in serach_better & search_posse.

```{r}
dt <- holes_2d_better_max_tries %>%
  filter(info != "interpolation") %>% 
  mutate(id = row_number())

p1 <- dt %>%
  ggplot(aes(x = as.factor(tries), y = alpha, col = as.factor(alpha))) +
  geom_jitter() +
  geom_line(data = dt %>% group_by(tries) %>% filter(index_val == max(index_val)),
            aes(group = 1)) + 
  theme(legend.position = "none")

dt <- holes_2d_pos %>%
  filter(info != "interpolation") %>% 
  mutate(id = row_number())

p2 <- dt %>%
  ggplot(aes(x = as.factor(tries), y = alpha, col = as.factor(alpha))) +
  geom_jitter() +
  geom_line(data = dt %>% group_by(tries) %>% filter(index_val == max(index_val)),
            aes(group = 1))  + 
  theme(legend.position = "none")

## Explore matrix parameter

### 2020-05-19 paper/paper.tex
write GOG; explore post-run diagnostics using vis

Below listed several issues in projection pursuit optimisation. Some of
them are general problems in optimisation literature, while others are
more specific for PP optimisation.

\begin{itemize}
\item
  \emph{Finding global maximum}: Although finding local maximum is
  relatively easy with developed algorithms, it is generally hard to
  guarantee global maximum in a problem where the objective function is
  complex or the number of decision variables is large. Also, there are
  discussions on how to avoid getting trapped in a local optimal in the
  literature.
\item
  \emph{optimising on non-smooth function}: When the objective function
  is non-differentiable, derivative information can not be obtained.
  This means traditional gradient- or Hessian- based methods are not
  feasible, stochastic optimisation method could be an alternative to
  solve these problems.
\item
  \emph{computation speed}: The optimisation procedure needs to be fast
  to compute because tours produces real-time animation of the projected
  data.
\item
  \emph{consistency result in stochastic optimisation}: In stochastic
  algorithm, researchers usually set a seed to ensure the algorithm
  producing the same result for every run. While this practice supports
  reproducibility, less efforts has been made to guarantee different
  seeds will provide the same result.
\item
  \emph{high-dimensional decision variable}: In projection pursuit, the
  decision variable is the entry in the projection matrix, which is
  usually high-dimensional. Researcher would be better off if they can
  understand the relative position of different projection matrix in the
  high-dimensional space.
\item
  \emph{role of interpolation in PP optimisation}: An optimisation
  procedure usually involves iteratively finding projection bases that
  maximise the index function, while tour requires geodesic
  interpolation between these bases to produce a continuous view for the
  users. It would be interesting to see if the interpolated bases could,
  in reverse, help the optimisation reach faster convergence.
\end{itemize}

@@

\hypertarget{recording-the-guided-tour}{%
\section{Recording the guided tour}\label{recording-the-guided-tour}}

@@

@@

\hypertarget{add-something-about-general-vis}{%
\subsection{add something about general
vis}\label{add-something-about-general-vis}}

The creation of the global object facilitates the diagnostics of the
optimisation in the projection pursuit guided tourr. Different
diagnostic plots could be made to understand the optimisation
\textbf{{[}pretty cheesy here{]}}

@@

\hypertarget{index-vs-time-plots}{%
\subsection{index vs time plots}\label{index-vs-time-plots}}

The tracing plot is useful to explore the index value. Given a global
object created, \texttt{explore\_trace\_all()} plots the index value of
all the bases.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{holes_2d_geo }\OperatorTok{%>%}\StringTok{ }\KeywordTok{explore_trace_all}\NormalTok{(}\DataTypeTok{magnify =} \OtherTok{TRUE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{holes_2d_geo }\OperatorTok{%>%}\StringTok{ }\KeywordTok{explore_trace_interp}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\includegraphics{paper_files/figure-latex/unnamed-chunk-7-2.pdf}

\hypertarget{target-basis-vs-interpolation-steps-index-vs-time}{%
\subsection{target basis vs interpolation steps, index vs
time}\label{target-basis-vs-interpolation-steps-index-vs-time}}

\hypertarget{low-d-representation-pca}{%
\subsection{low-d representation, PCA}\label{low-d-representation-pca}}

@@

@@

\includegraphics{paper_files/figure-latex/unnamed-chunk-10-1.pdf}

>>>>

Below listed several issues in projection pursuit optimisation. Some are
general optimisation problems, while others are more specific for PP
optimisation.

\begin{itemize}
\item
  \emph{Finding global maximum}: Although finding local maximum is
  relatively easy with developed algorithms, it is generally hard to
  guarantee global maximum in a problem where the objective function is
  complex or the number of decision variables is large. Also, there are
  discussions on how to avoid getting trapped in a local optimal in the
  literature.
\item
  \emph{optimising non-smooth function}: When the objective function is
  non-differentiable, derivative information can not be obtained, which
  means traditional gradient- or Hessian- based methods are not
  feasible. Stochastic optimisation method could be an alternative to
  solve these problems.
\item
  \emph{computation speed}: The optimisation procedure needs to be fast
  to compute since tours produces real-time animation of the projected
  data.
\item
  \emph{consistency result in stochastic optimisation}: In stochastic
  algorithm, researchers usually set a seed to ensure the algorithm
  producing the same result for every run. This practice supports
  reproducibility, while less efforts has been made to guarantee
  different seeds will provide the same result.
\item
  \emph{high-dimensional decision variable}: In projection pursuit, the
  decision variable includes all the entries in the projection matrix,
  which is high-dimensional. Researcher would be better off if they can
  understand the relative position of different projection matrix in the
  high-dimensional space.
\item
  \emph{role of interpolation in PP optimisation}: An optimisation
  procedure usually involves iteratively finding projection bases that
  maximises the index function, while tour requires geodesic
  interpolation between these bases to produce a continuous view for the
  users. It would be interesting to see if the interpolated bases could,
  in reverse, help the optimisation reach faster convergence.
\end{itemize}

@@

\hypertarget{iterative-algorithm-and-its-diagnostics}{%
\section{Iterative algorithm and its
diagnostics}\label{iterative-algorithm-and-its-diagnostics}}

@@

\hypertarget{diagnostics}{%
\subsection{Diagnostics}\label{diagnostics}}

Visualisatioin has been widely used for exploring and understanding
data. Visualisation presents information in a graphicial manner and
often allows people to see information they would otherwise not seen in
the reporting of numerical summarisation. Visual diagnostics can be
real-time or post-run. Real time diagnostic directly uses the data
produced in the algorithm to produce visual representation and thus
doesn't need to store the data. This section focuses on the definition
and production of post-run diagnoistics and the next section discusses
real-time diagnostics.

Post-run diagnostics requires the data produced during the algorithm to
be stored/ saved in order to produce plot diagnostics.

The graphical system in R is established based on the conception gramma
of graphic \citep{wickham2010layered}, where a graphic is defined using
stacked layers in a coordination system. A layer includes 1) the dataset
that powers the plot; 2) a geometric object that represents the visual
shape of the plot and 3) relevant statistical transformation if needed.
An important concept in the gramma of graphic is \emph{aesthetic
mapping}. Aesthetic mapping links the variable in a dataset to
information needed to produce a geometric object. For example, we map
one variable on the x-axis and another on the y-axis to create a
scatterplot. To create a boxplot, we first map one variable on the
x-axis and then map the five point summary of another variable on the
y-axis. This computation of five point summary from the origin variable
is statistical transformation. This definition of graphic through layers
provides advantages to produce complex plots since all the plots,
however complex, can be decomposed into basic geometric objects shaped
by the variable supplied.

This idea of decompositing a graph to basic elements inspires me to
characterise the diagnostics of iterative algorithm in a similar
fashion. The optimisation in many machine learning algorithms these days
is iterative in nature, while remains as a black box. Being able to
diagnose it visually allows researchers to have the tool to unfold the
myth and thus provides more understand to the algorithm.

The concept of gramma of graphic requires a dataset to be supplied in
making a plot, thus a global object needs to be created in the iterative
algorithm. The variables will be mapped into element of a graphic to
explore and thus should contain all the parameters of interest. The next
section shows how a global object is created in projection pursuit
guided tour.

@@

Given all the information of interest in a global object, the next thing
is to design its visual representation that can diagnose our algorithm.
In an iterative algorithm, one would be interested to know how one
parameter changes as the algorithm iterates. The parameter could be
could be the decision variable, the value of the optimisation function
or other parameter that facilitate the algorithm. In projectio pursuit
guided tour, apart from the decision variable projection basis, the
value of index function (\texttt{index\_val}), we are also interested to
explore the effect the different searching methods, the neighbourhood
parameter alpha, and the stage a particular observation is in
(\texttt{info}). These are the variables that will be mapped into the
diagnostic plot. The global object also has its time series nature since
the observations are recorded as the algorithm progresses and thus can't
be switch in rows. This time series structure is always hierachical and
nested since each row can be labelled with the smallest unit \texttt{id}
and up by the iterative structure of the algorithm. Take our example, in
the global object, each row has an \texttt{id} label which is the
smallest unit the observation is ordered. A larger ordering unit is
\texttt{tries} since it is updated everytime a new target basis is
found. A nested ordering unit is \texttt{loop}, which increases by one
as searching method iterates and starts over at a new \texttt{tries}.
These features explain the definition of the global object for
projection pursuit guided tour in Figure @ref(fig:glb-obj).

\begin{figure}
\includegraphics[width=1\linewidth,height=0.2\textheight]{/Users/hzha400/Documents/3.PhD/paper-tour-vis/figures/global_obj} \caption{this is xxxx}\label{fig:glb-obj}
\end{figure}

@@

\hypertarget{explore-scalar-parameters}{%
\subsection{Explore scalar parameters}\label{explore-scalar-parameters}}

The most interesting parameter to explore is the value of objective
function. Given the structure of projection pursuit guided tour
algorithm, whatever searching method we use, we could roughly divide the
observation into three category: searching, updating and interpolating
points.

\begin{itemize}
\item
  \emph{Searching points} include the observations that ones recorded
  during the trials and errors in the searching algorithm to find the
  target basis. In one \texttt{tries}, there could be only a few
  searching points while towards the end of the algorithm, they can
  easily go to hundreds.
\item
  \emph{Updating points} are the observations for the target points and
  there are only one points per \texttt{tries}. We use ``all searching
  points'' to refer to the collection of both searching and updating
  points.
\item
  \emph{interpolation points} exist specifically in the guided tour in
  order to provide continuous animated view from one target basis to
  another, thus they are not included in the searching procedure. There
  are multiple points in one tries but it doesn't have \texttt{loop}
  value.
\end{itemize}

\hypertarget{explore-all-searching-points}{%
\subsubsection{Explore all searching
points}\label{explore-all-searching-points}}

As mentioned previously, the largest feature of exploring searching
points is its uncertainty in the number per \texttt{tries}. This makes
it difficult to map \texttt{id} on the x-axis since the first few tries
that can be informative to the evolving of the algorithm occupies a
small number of points on the graph while the large less informative
search points towards the end occupies the vast majority of the plot
space.

This motivates the use of summarised statistics. At each iteration,
rather than knowing the value of \emph{every} points, we are more
interested to know a general summary of all the points and more
importantly, the point with the largest \texttt{index\_val} since it is
the one that prescribe the interpolation and future search. Therefore,
boxplot is a suitable candidate.

However, boxplot doesn't tells us the number of point in each box. By
showing boxplot for all \texttt{tries}, we lose information on how long
it takes for the search to find the target basis. We may still want to
show the exact points of every point if there are only a few points.
Therefore a cutoff point is placed as an argument to decise when to
switch from point geometry to boxplot geometry.

This design is easy to implement with the concept of gramma of graphic.
With the idea of layed gramma, we only need to subset the data and map
it onto the either a point geometry or boxplot geometry. We can also add
a layer with line geometry that connect the points with the largest
\texttt{index\_val} in each tries. This would show us which
\texttt{tries} has the largest improvement.

A comparison of using scatter plot (all point geometry) and my new
design is shown in Figure @ref(fig:explore-all-search). As we can see
the points for the first few tries on hte scatter plot are all squeezed
in a tiny region, being nearly unseeable. While the plot on the right
balances out the points in each \texttt{tries}. By linking the updating
points for each \texttt{tries}, we observe that the largest improvement
occurs in \texttt{tries\ =\ 5} where the number of searching points
dramastically increased from 11 points in \texttt{tries\ =\ 4} to 86
points in \texttt{tries\ =\ 5}.

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/explore-all-search-1.pdf}
\caption{This is xxx}
\end{figure}

\hypertarget{explore-only-interpolation-points}{%
\subsubsection{Explore only interpolation
points}\label{explore-only-interpolation-points}}

While mapping \texttt{tries} to the x axis allows for viewing the
magnitude of the interpolation and also its density, we can't really see
the curvature of the interpolated path. Think this would be important
when the index is no longer smooth and the interpolation will jump up
and down. Thus the geom\_point + geom\_line specification is still
preferred.

EXAMPLE: prevention on the decrese of interpolated value - interruption

EXAMPLE: comparison of interpolation in noisy index function

@@

\hypertarget{adding-more-variables-to-the-mapping}{%
\subsubsection{Adding more variables to the
mapping}\label{adding-more-variables-to-the-mapping}}

For now we only include the iterator and \texttt{index\_val} in the
mapping of the plot, while more paramters of interest could be added to
explore the effect their effect.

EXAMPLE: polishing - add method : compare with max.tries and without for
search\_better.

EXAMPLE: add alpha: compare the cooling system of the neighbourhood
parameter in serach\_better \& search\_posse.

\hypertarget{explore-matrix-parameter}{%
\subsection{Explore matrix parameter}\label{explore-matrix-parameter}}

@@

\includegraphics{paper_files/figure-latex/unnamed-chunk-9-1.pdf}

@@

\includegraphics{paper_files/figure-latex/unnamed-chunk-11-1.pdf}
